Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-08 paper/structureScene.tex
\newcommand*{\vs}{vs.\@\xspace}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}

@@

\subsection{Early vs. late temporal integration}
Owing to the scarcity of salient events in many natural scenes,
fine-grained classification is only made
possible by integrating signal information over a long temporal context.
Indeed, whereas a few seconds are often sufficient to recognize a speaker,
a musical instrument, or a genre, it may require up to 30 seconds
to disambiguate auditory scenes which share part of their semantic content, \eg a train from a subway station or a quiet street from a park.
Depending on whether aggregation is performed in feature space or in decision space, the corresponding method is referred to as early or late integration.

@@

\ml{VL 2 colonnes}

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

@@

\subsection{Early \vs late temporal integration}
Owing to the scarcity of salient events in many natural scenes,
fine-grained classification is only made
possible by integrating signal information over a long temporal context.
Indeed, whereas a few seconds are often sufficient to recognize a speaker,
a musical instrument, or a genre, it may require up to 30 seconds
to disambiguate auditory scenes which share part of their semantic content, \eg a train from a subway station or a quiet street from a park.
Depending on whether aggregation is performed in feature space or in decision space, the corresponding method is referred to as early or late integration.

@@

\subsection{Role of logarithmic compression}

\subsection{Time scattering \vs time-frequency scattering}
